A Partitioning Algorithm for Maximum Common Subgraphs\thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant numbers EP/K503058/1 and EP/M508056/1]}

### 2017-02-14 paper/paper.tex
Some writing about experiments

\paragraph{No vertex labels, no edge labels, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis) against number of problem instances solved (y-axis). There are five contours: 
the clique encoding \cite{DBLP:conf/cp/McCreeshNPS16}, CP-FC \cite{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS. 	What we see is that \McSplit\ is typically more than one order of magnitude better than its nearest competitor.

@@

\paragraph{Vertex labels, edge labels, directed} are in \cref{figure:33ved-cumulative}.

@@

\begin{figure}
    \centering
    \subfigure[][MCS unlabelled unconnected instances] {
        \centering
        \includegraphics*{gen-graph-plain-cumulative.pdf}
        \label{figure:plain-cumulative}
    }

    \subfigure[][MCS 33\% vertex and edge labelled directed instances] {
        \centering
        \includegraphics*{gen-graph-33ved-cumulative.pdf}
        \label{figure:33ved-cumulative}
    }
    \caption{Cumulative runtimes}\label{figure:mcs-cumulative}
\end{figure}

@@

    \subfigure[][MCS 33\% vertex and edge labelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-33ve-connected-cumulative.pdf}
        \label{figure:33ve-connected-cumulative}
    }
    \caption{Cumulative runtimes, connected variant}
    \label{figure:mcs-connected-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative runtimes, SIP instances}\label{figure:sip-cumulative}
\end{figure}

>>>>

\paragraph{No vertex labels, no edge labels, undirected}
\cref{figure:plain-cumulative} shows a plot of cumulative run times (x-axis)
against number of problem instances solved (y-axis).  There are five contours:
the clique encoding \cite{DBLP:conf/cp/McCreeshNPS16}, CP-FC
\cite{DBLP:conf/cp/NdiayeS11}, \McSplit\, AND TWO OTHERS.  WE NEED CITATIONS
FOR THESE AND ALSO NEED TO CLEAN UP THE LABELS ON THE GRAPHS.  We may compare
the speed of two algorithms using the horizontal distance between their curves.
For example, we could solve 2000 of the 4110 unlabelled undirected instances
using the \McSplit\ algorithm if a time limit of 0.5 seconds per instance were
imposed.  Its nearest competitor, CP-FC, would require a time limit of over 24
seconds per instance to solve the same number of instances.  For any given
number of instances, \McSplit\ is comfortably more than an order of magnitude
faster than its nearer competitor.  Moreover, there are few instances in this
set for which \McSplit\ is not the fastest solver; of the 3506 instances that
could be solved by at least one of \McSplit, CP-FC and clique in less than than
1000 seconds, there were only 126 instances on which \McSplit\ was not strictly
faster than the other two solvers.

\paragraph{Vertex labels, edge labels, directed}
Cumulative run times for this class of instances are in \cref{figre:33ved-cumulative}.
Again, \McClique\ is over an order of magnitude faster than the best CP algorithm,
which is CP-MAC in this case.  The clique encoding, however, outperforms the other
algorithms on these labelled instances, except in the easy region at the left
of the graph.

@@

@@

\begin{figure}
    \centering
    \subfigure[][MCS unlabelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-plain-cumulative.pdf}
        \label{figure:plain-cumulative}
    }

    \subfigure[][MCS 33\% vertex and edge labelled directed instances] {
        \centering
        \includegraphics*{gen-graph-33ved-cumulative.pdf}
        \label{figure:33ved-cumulative}
    }
    \caption{Cumulative run times}\label{figure:mcs-cumulative}
\end{figure}

@@

    \subfigure[][MCS 33\% vertex and edge labelled undirected instances] {
        \centering
        \includegraphics*{gen-graph-33ve-connected-cumulative.pdf}
        \label{figure:33ve-connected-cumulative}
    }
    \caption{Cumulative run times, connected variant}
    \label{figure:mcs-connected-cumulative}
\end{figure}

\begin{figure}
    \centering
    \includegraphics*{gen-graph-sip-cumulative.pdf}
    \caption{Cumulative run times, SIP instances}\label{figure:sip-cumulative}
\end{figure}
